Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-13 paper/paper.tex
Abstract v1

\end{abstract}

>>>>

  So far, for this natural problem, the best known deterministic algorithm was $O(k^2\cdot \ell^2)$-competitive, and the best known lower bound was $\Omega(k)$ for the competitive ratio of any deterministic algorithm that used the reduction from the caching problem.
  In this paper, we significantly improve this lower bound to $\Omega(k\cdot \ell)$.
  Furthermore, we provide a $O(k\cdot \ell)$-competitive algorithm for the scenario, where the perfect partition of input exists.
\end{abstract}
